Applied Measure Theory for Probabilistic Modeling

### 2022-05-20 paper/paper.tex
Update paper/paper.tex
Co-authored-by: Moritz Schauer <moritzschauer@web.de>

%While it does uniquely identify a probability density, it is not a probability density.

@@

One further such space that deserves mention is traditionally denoted $\Omega$. This is an abstract space connected to the real-world notion of \emph{probability}, which we denote as $\operatorname{Prob}$.
Computationally, $\Omega$ can be considered to be the set of possible states of a random number generator \verb|rng::AbstractRNG|, which is the source of computational randomness.

>>>>

@@

One further such space that deserves mention is traditionally denoted $\Omega$. This is an abstract space connected to the real-world notion of \emph{probability}, which we denote as $\operatorname{Prob}$.
Computationally, $\Omega$ can be considered to be the set of possible initial states of a random number generator \verb|rng::AbstractRNG|, which is the source of computational randomness.
